Hospital Information Technology and Physician Response

### 2022-02-23 Table Code/overall stats.tex

\footnotesize
\caption{\footnotesize Summary Statistics}
\vspace{-2mm}
\begin{tabular}[t]{lcccc}
\toprule
Variable & Mean & Std. Dev. & Min & Max\\
\midrule
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Static}}\\
\hspace{1em}Average Hospital Operating Days  & 364.89 & 5.11 & 41 & 366\\
\hspace{1em}Average Size of Hospitals Worked With (Beds)  & 373.12 & 252.40 & 10 & 2574\\
\hspace{1em}Female  & 0.31 & 0.46 & 0 & 1\\
\hspace{1em}Medical School Grad. Year  & 1993 & 10.04 & 1949 & 2008\\
\hspace{1em}Number of Hospitals Worked With  & 1.87 & 1.30 & 1 & 40\\
\hspace{1em}Number of Systems Worked With  & 1.48 & 0.77 & 1 & 13\\
\addlinespace[0.3em]
\multicolumn{5}{l}{\textbf{Dynamic}}\\
\hspace{1em}Exposure to an EHR  & 0.70 & 0.46 & 0 & 1\\
\hspace{1em}Fraction of Hospitals with EHR  & 0.56 & 0.44 & 0 & 1\\
\hspace{1em}Number of Patients & 620.54 & 988.74 & 0 & 74639\\
\bottomrule
\end{tabular}

>>>>

\begin{table}[h]
\caption{Summary Statistics}
\centering
\begin{tabular}[t]{lrrrrr}
\toprule
Variable & N & Mean & Std. Dev. & Min & Max\\
\midrule
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Outcomes}}\\
\hspace{1em}Ever Retire & 403020 & 0.02 & 0.13 & 0 & 1\\
\hspace{1em}Fraction Patients in Office & 403020 & 0.31 & 0.36 & 0 & 1\\
\hspace{1em}Work in an Office & 403020 & 0.57 & 0.49 & 0 & 1\\
\hspace{1em}Change Zip Codes & 372357 & 0.08 & 0.28 & 0 & 1\\
\hspace{1em}Number of Patients & 403020 & 2220.46 & 3207.08 & 0 & 199765\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Treatment}}\\
\hspace{1em}Exposure to an EHR & 403020 & 0.64 & 0.48 & 0 & 1\\
\hspace{1em}Exposure to an EHR (Low Integration) & 403020 & 0.42 & 0.49 & 0 & 1\\
\hspace{1em}Fraction of Hospitals with EHR & 403020 & 0.52 & 0.46 & 0 & 1\\
\addlinespace[0.3em]
\multicolumn{6}{l}{\textbf{Characteristics}}\\
\hspace{1em}Age & 403002 & 47.71 & 9.38 & 23 & 89\\
\hspace{1em}Female & 403020 & 0.31 & 0.46 & 0 & 1\\
\hspace{1em}Number of Hospitals Worked With & 403020 & 1.49 & 0.83 & 1 & 20\\
\hspace{1em}Number of Systems Worked With & 403020 & 1.30 & 0.59 & 1 & 8\\
\bottomrule
\end{tabular}
\end{table}
